---
title: "Hello World"
author: "Dr Massimiliano Canzi"
format: 
  revealjs:
    multiplex: true
    transition-speed: fast
    transition: fade
    background-transition: fade
    chalkboard: true
    slide-number: true
    show-slide-number: print
    touch: true
    controls: true
    theme: theme-mc.scss
    incremental: true
    footer: "`massimiliano.canzi@uni-konstanz.de` | Room G114, **Universität Konstanz**. Universitätstr. 10, 78467 Konstanz DE"
---

```{r}
#| include: false
library(tidyverse)
```

## 

Data analysis  
From hypothesis to tests  
Stats for linguists' quest  

~ `ChatGPT`

# Greetings :~)

## Who

Dr Massimiliano (__Max__) Canzi

- `PhD`: University of Manchester 
- `MSc`: University of York 
- `MA`: University of Manchester 
- `BA`: University of Milan

__Interests__: `speech perception`, `rstats`, `quantitative linguistics`, `experimental linguistics`, `speech production`, 
`forensic speech science` 

## Who

Dr Massimiliano (__Max__) Canzi

- `What PMN? Processing phonological mismatch in semantics-free speech perception`
- `Do somatic features of a speaker mediate the perception of the speaker's voice?`
- `A quantitative analysis of acoustic differences between neutral and loud speech`

## Who

Ilaria Venagli

- `PhD`: (__Currently__) University of Konstanz
- `MA`: University of Venice (Ca' Foscari)
- `BA`: University of Milan 

## Who

Ilaria Venagli 

- 
- `The Mental Representations of Crosslinguistically Different Structures. The Case of Si-Causative Passives in Italian- English Late Bilinguals`

## Who 

`... ARE YOU?`

## Supervision

- Maximum `two dissertations` as first supervisor, per semester 
- Maximum `three dissertations` as second supervisor, per semester 

. . .

 `get in touch` if you are an __SLP__ students looking for an internal internship
 
## Structure 

- `One` weekly lecture (_Thu, 17:00_). `One` weekly tutorial (_Fri, 15:30_)
- `One` final assignment (worth 80\% of final grade).  `One` midterm (worth 20\% of final grade)
- `80%` attendance / midterm are required to submit final exam 
- `NEW!` Optional, extra step-mark* for writing a __Wiki__ article. Optional, extra step-mark* for winning `Kahoot`

::: aside
\* `1.3` instead of `1.7`, `2.0` instead of `2.3`. `5` is not affected. `5` in final exam results in outright __FAIL__.
:::

## Slides

Slides are made in `RStudio`, using `Quarto` and `RevealJS`

. . .

Each week you will receive:

- The `slides` (as a .html file)
- The `code` for the slides (as a .qmd file, if applicable)
- Weekly `exercises`

## Resources

Here, we use `Discord` 

- You can join the `Discord` server through this link: 
- Use the `homework-help` channel for any content-related question first. 
- Use other channels too to keep up-to-date. 

`Ilias` only used for the submission of the final assignment. 

## Final Assignment

- You will conduct an extensive `data analysis` of linguistic data
- You will `write-up` a report of the analysis, including a step-by-step commentary and a discussion of the findings
- You will do that in the style of a `scientific experimental paper`
- You will submit your paper as one `single html` / pdf `file`, rendered from Quarto
- The file will contain the `text` of your paper alongside the `code` of your analysis

## Final Assignment 

You are `NOT` allowed to work in groups throughout the entire realisation of the final exam. Each student `will work independently` and submit their own paper. 

## Final Assignment 

_The words you use should be your own_  
_Don't plagiarise or take "on loan"_  
_Cause there's always someone, somewhere_  
_With a big nose, who knows_  
_And who trips you up and laughs_  
_When you fall_  
  
`The Smiths`

## Midterm 

Multiple-choice exam, when: __TBD__

## Book 

Winter, B. (2019). `Statistics for linguists: An introduction using R`. Routledge.

## Syllabus

Roughly --- `each week is one Chapter`.

- Week `2`: Chapter `2`
- Week `3`: Chapter `3`
- Week `4`: Chapter `4`
- Week `5`: Chapter `5`
- ...

## The meat and potatoes

- R
- RStudio
- Quarto 

## `swirl` 

`swirl` is an `R` package that teaches you to use `R`.. in `R`. You can learn more at the project homepage [__here__](https://swirlstats.com/students.html). You install `swirl` like you install any other `R` package. You need to do this only once. 

```{r}
#| eval: false
#| echo: true
install.packages("swirl")
```

To use `swirl` when you open __RStudio__, import the package and start a new `swirl` session. 

```{r}
#| eval: false
#| echo: true
library(swirl)
swirl()
```

## `swirl`

The `swirl` package contains dozens of interactive tutorials for learning `R`, from more basic exercises to more complex modelling tasks. You will be given specific tutorials to complete as part of your homework. You are very encouraged to complete these tasks and explore more on your own. 

## `tidyverse`

`tidyverse` is a new _dialect_ of `R` _(the standard variety being base `R`)_

. . .

`tidyverse` is a series of `R` packages and functions created by [__H. Wickham__](https://twitter.com/hadleywickham) and colleagues that substitute many of the base `R` alternatives, while at the same time being easier to write, read and reproduce. However, there is no way around knowing the basics of base `R` before we dive into the `tidyverse`. 

## Why Quantitative Methods?

Discuss...

## Objective or Subjective?

Discuss...

## You will

- Acquire `fundamental concepts` to conducting statistical analyses in R. 
- Learn fundamental concepts of `regression modelling`
- Learn to apply the above to `real linguistic data`

## Homework 

- Read `Chapter 2` of Winter 2019
- Complete exercises in the Chapter
- Ask questions on `Discord` if you have any 

## And now

. . .

Let's jump into `RStudio` for an overview
